### 2024-06-15 conteudo/tool/architecture.tex
Add more work, 14/06

The Function Parser receives the input codebase and transforms it into the temporary codebase. The Function Parser iterates through
every source code file from the programming language it support and use a specific programming languague's function 
extractor to extract
every function in the file, for each function extracted we create a new source code file and a metadata file in the temporary codebase
which is represented by the pair \textbf{<source code file, function extracted>}, which represents the source code file the 
function is extracted from and the 
proper function. The new source code file only contains the source code from the function it represents, while the metadata file 
contains extra relevant information such as function name, the line the function it began to be declared in the original souce code 
file and the line the function's body ends in the original source code file. The programming language we support at the moment 
is C and Java. Can be found a example of a transform of a source code in the (CREATE APENDIX AND ADD HERE).

@@

\begin{itemize}
  \item \textbf{C}:
  \item \textbf{Java}:
\end{itemize}

@@

>>>>

The Function Parser receives the input codebase and transforms it into the temporary codebase. The Function Parser iterates through
every source code file from the programming language it support and use a specific programming languague's function 
extractor to extract
every function in the file, for each function extracted we create two new source code files and a metadata file in the temporary codebase
which is represented by the pair \textbf{<source code file, function extracted>}, which represents the source code file the 
function is extracted from and the 
proper function. The first new source code file contains the function's body from the function it represents, while the other
new source code file contains the function's signature, the metadata file 
contains extra relevant information such as function name, the line the function signature starts in the original souce code 
file and the line the function's body ends in the original source code file. The programming language we support at the moment 
is C and Java. Can be found a example of a transform of a source code in the Figure (CREATE APENDIX AND ADD HERE).

@@

\begin{itemize}
	\begin{item}
		\textbf{C}:
	\end{item}
	\begin{item}
		\textbf{Java}:
	\end{item}
\end{itemize}

\subsection{Temporary codebase}

The temporary codebase is a transformation of the input codebase done by the Function Parser, every function in the input codebase
is represented in the temporary codebase as three files. There are description of each file below and an example of each can found
in the figure (CREATE FIGURE AND ADD HERE).

\begin{itemize}
	\begin{item}
		\textbf{Header file}: This file contains the signature of the function it represents;
	\end{item}
	\begin{item}
		\textbf{Source file:} This file contains the body of the function it represents;
	\end{item}
	\begin{item}
		\textbf{Info file:} This file contains metadata of the function. The information this file contains is:
		the function name, the file name that has the function, the relative path of the file related to the input codebase, 
		the line that the function's signatures starts, the line that the functions body starts, the line that the function's body 
		ends and if there is a line break between the end of the function's signature and the start of the function's body.

	\end{item}
\end{itemize}

There is a example of each file in the Appendix

@@

The Code Duplication Database is a text file that contains the duplicated pairs of functions found by the Code Duplication Finder, 
the first line of the file contains a number that represents the number of the duplicated pairs, after that, there is 
a line of each duplicated pairs that contains the path of the functions in the temporary codebase and the similarity metric of the 
pair. A example of the Code Duplication Database can be found in the figure (ADD FIGURE HERE).
